A Study of the Effectiveness of Usage Examples in REST API Documentation

### 2017-03-19 controlled_study.tex
fix typo
add preamble for related work

\textbf{T4: Find total posts tasks.} This task requires the participants to use the API to find a total number of posts. Participants need to use the inputs I1-2 and inspect the HTTP response headers to successfully complete this task. This task allows us to understand how API client developer productivity is affected with respect to missing examples about HTTP response headers in the API documentation.

@@

\section{Related Work}
\label{sec:related_work}
\subsubsection{API Learning Obstacles}
  Researchers have published several papers on the topic of API learning obstacles. Robillard et al. used a mixed approach of surveys and in-person interviews with professional software engineers to understand the API learning obstacles \cite{Robillard_what_makes} \cite{Robillard_a_field_study}. They found that many obstacles for API learnabilty were related to API documentation and five impactful factors for API documentation as follows: documentation of intent, code examples, matching APIs with scenarios, penetrability of the API, and format and presentation. Uddin and Robillard surveyed 323 professional software engineers to understand the different ways in which a piece of documentation can be unfit for purpose \cite{g_uddin}. They identified ambiguity, incompleteness, and incorrectness as the three severest problems that lead API documentations to fail to answer the information needs of developers. Duala-Ekoko and Robillard performed a study with twenty programmers to understand the types of questions that developers have while using an unfamiliar API \cite{Duala-Ekoko:2012:AAQ:2337223.2337255}. They categorized the API related information needs into twenty generic questions that can be used to analyze the quality of API documentation. Myers et al. performed a study of enterprise SOA API usability and found that the study participants had limited success finding the relevant API elements to perform an API task \cite{Myers_study}. Among other factors, they recommended providing code examples in the API documentation to help API client developers with sample solutions to different patterns of API tasks.

>>>>

\textbf{T4: Find total posts task.} This task requires the participants to use the API to find a total number of posts. Participants need to use the inputs I1-2 and inspect the HTTP response headers to successfully complete this task. This task allows us to understand how API client developer productivity is affected with respect to missing examples about HTTP response headers in the API documentation.

@@

\section{Related Work}
\label{sec:related_work}

In this section, we discuss the existing research on the relationship between API usability and usage examples. To this regard, we summarize the related work on APIs from the sub-areas of API learning obstacles, using crowd-sourced API examples, measuring API usability, and controlled studies on the impact of usage examples on API usability.

\subsubsection{API Learning Obstacles}
  Researchers have published several papers on the topic of API learning obstacles. Robillard et al. used a mixed approach of surveys and in-person interviews with professional software engineers to understand the API learning obstacles \cite{Robillard_what_makes} \cite{Robillard_a_field_study}. They found that many obstacles for API learnabilty were related to API documentation and five impactful factors for API documentation as follows: documentation of intent, code examples, matching APIs with scenarios, penetrability of the API, and format and presentation. Uddin and Robillard surveyed 323 professional software engineers to understand the different ways in which a piece of documentation can be unfit for purpose \cite{g_uddin}. They identified ambiguity, incompleteness, and incorrectness as the three severest problems that lead API documentations to fail to answer the information needs of developers. Duala-Ekoko and Robillard performed a study with twenty programmers to understand the types of questions that developers have while using an unfamiliar API \cite{Duala-Ekoko:2012:AAQ:2337223.2337255}. They categorized the API related information needs into twenty generic questions that can be used to analyze the quality of API documentation. Myers et al. performed a study of enterprise SOA API usability and found that the study participants had limited success finding the relevant API elements to perform an API task \cite{Myers_study}. Among other factors, they recommended providing code examples in the API documentation to help API client developers with sample solutions to different patterns of API tasks.
